Prospective testing for the prevalence or transience of a shock effect over a set time horizon before it occurs

### 2022-06-14 prevalence_testing/postshocktest2022draft.tex
addition of dual shock analysis

\vspace*{0.5cm}\noindent\textbf{Note}\vspace*{0.5cm}

@@

\textcolor{red}{We motivate a similar approach within our prevalence testing framework. The idea is to again separate out the financial and oil supply time series and add these series together which will create a new donor pool consisting of series which incorporate a dual shock whose behavior can be assessed with our methodology. As in \cite{lin2021minimizing} the oil supply shock donor pool consists of the single November 27, 2014 series; and the financial shock donor pool consists of the remaining two series. These added series which account for a potential dual shock take the following form where the subscript $o$ refers to the single November 27, 2014, the subscript $j$ indexes the other series, and $T_o = T_j$ and $T^*_o = T^*_j$}
\begin{equation} \label{eq:dualshock}
\begin{split}
  z_{j,t} &= y_{o,t} + y_{j,t} \\
  	&= \bar{\eta}_j + (\phi z_{j,t-1} +\theta_{o,t-1}'\x_{o,t-1} +\theta_{j,t-1}'\x_{j,t-1})(1 - \bar{D}_t) \\
  	&\qquad + (\bar{\alpha}_j + \tilde{\phi} z_{j,t-1} + \tilde{\theta}_{o,t-1}'\x_{o,t-1}   + \tilde{\theta}_{j,t-1}'\x_{j,t-1})\bar{D}_t + \bar{\varepsilon}_t,
\end{split}
\end{equation}
where $\bar{\eta}_j = \eta_o + \eta_j$, $\bar{\alpha}_j = \alpha_o + \alpha_j$, $D_t = D_{0,t} = D_{j,t}$, and $\bar{\varepsilon}_t = \varepsilon_{0,t} + \varepsilon_{j,t} + D_t(\varepsilon_{\alpha,o} + \varepsilon_{\alpha,j})$. The model \eqref{eq:dualshock} is then a regression model with a heterogeneous error structure, the error distribution post-shock differs from the error distribution pre-shock. All model parameters are estimable in \eqref{eq:dualshock}. However, aggregation strategies are slightly different for this model since covariates are included for two separate series.

We now examine distance-based weighting for model \eqref{eq:dualshock}. Consider a weight vector $\textbf{W}^d \in \R^{n-1}$ with elements $w_i \in [0,1]$ that satisfy $\sum_i w_i = 1$. Construct $\X_1^d = (\x_{1,T^*_1+1}', \; \x_{1,T^*_1+1}')$, $\X^d \in \R^{n-1 \times 2p}$ with rows $(\x_{o,T^*_o+1}', \; \x_{j,T^*_j+1}')$, and $\hat{\X}_1^d(\textbf{W}) = \textbf{W}^{d'}\X^d$. Then the optimal weights satisfy 
$$
  \textbf{W}^{d*} = \text{arg min}_{\textbf{W} \in \mathcal{W}} \|\X_1^d - \hat{\X}_1^d(\textbf{W})\|_{2p}
$$
where $\mathcal{W}$ is the set of all allowable weight vectors.

\begin{table}[H]
	\caption{Results for Conoco Philips dual shock ($n=2$), $\mbf{W}^* = (0.756, 0.244)$ from scaled covariates} \label{coptable}
\begin{center}
  \begin{tabular}{cccccccccr}
     $H$   &  $\hat{p}_1$ &   Vote (Correct?) & weighted Vote (Correct?)   \\
     \hline 
     2  & 1    & 0 (Yes) &0 (Yes)   \\ 
     4  & 1 & 0(Yes)  &0 (Yes)  \\ 
     6   & 1  &0 (Yes) & 0 (Yes) \\ 
     8   & 1  & 0 (Yes) & 0 (Yes)
  \end{tabular}
\end{center}	
\end{table}

>>>>

\subsubsection{Dual shock prevalence testing}

@@

\textcolor{red}{We motivate a similar approach within our prevalence testing framework. The idea is to again separate out the financial and oil supply time series and add these series together which will create a new donor pool consisting of series which incorporate a dual shock whose behavior can be assessed with our methodology. As in \cite{lin2021minimizing} the oil supply shock donor pool consists of the single November 27, 2014 series; and the financial shock donor pool consists of the remaining two series. These added series which account for a potential dual shock take the following form where the subscript $o$ refers to the single November 27, 2014, the subscript $j$ indexes the other series, and $T_o = T_j$ and $T^*_o = T^*_j$}
\begin{equation} \label{eq:dualshock}
\begin{split}
  z_{j,t} &= y_{o,t} + y_{j,t} \\
  	&= \bar{\eta}_j + (\phi z_{j,t-1} +\theta_{o,t-1}'\x_{o,t-1} +\theta_{j,t-1}'\x_{j,t-1})(1 - \bar{D}_t) \\
  	&\qquad + (\bar{\alpha}_j + \tilde{\phi} z_{j,t-1} + \tilde{\theta}_{o,t-1}'\x_{o,t-1}   + \tilde{\theta}_{j,t-1}'\x_{j,t-1})\bar{D}_t + \bar{\varepsilon}_t,
\end{split}
\end{equation}
where $\bar{\eta}_j = \eta_o + \eta_j$, $\bar{\alpha}_j = \alpha_o + \alpha_j$, $D_t = D_{0,t} = D_{j,t}$, and $\bar{\varepsilon}_t = \varepsilon_{0,t} + \varepsilon_{j,t} + D_t(\varepsilon_{\alpha,o} + \varepsilon_{\alpha,j})$. The model \eqref{eq:dualshock} is then a regression model with a heterogeneous error structure, the error distribution post-shock differs from the error distribution pre-shock. All model parameters are estimable in \eqref{eq:dualshock}. \textcolor{red}{Shock prevalence testing for $z_{j,t}$ is still conducted by comparing forecasts between adjusted and unadjusted conditional mean forecasts as illustrated in Section \ref{sec:multhor}}. However, aggregation strategies are slightly different for this model since covariates are included for two separate series.

We now examine distance-based weighting for model \eqref{eq:dualshock}. Consider a weight vector $\textbf{W}^d \in \R^{n-1}$ with elements $w_i \in [0,1]$ that satisfy $\sum_i w_i = 1$. Construct $\X_1^d = (\x_{1,T^*_1+1}', \; \x_{1,T^*_1+1}')$, $\X^d \in \R^{n-1 \times 2p}$ with rows $(\x_{o,T^*_o+1}', \; \x_{j,T^*_j+1}')$, and $\hat{\X}_1^d(\textbf{W}) = \textbf{W}^{d'}\X^d$. Then the optimal weights satisfy 
$$
  \textbf{W}^{d*} = \text{arg min}_{\textbf{W} \in \mathcal{W}} \|\X_1^d - \hat{\X}_1^d(\textbf{W})\|_{2p}
$$
where $\mathcal{W}$ is the set of all allowable weight vectors. \textcolor{red}{Note that if the model is correctly specified,   inference under this dual shock setup should work well if $\{y_{o,t}\colon t= 1, \ldots, T_0\}$ and $\{y_{j, t} \colon j = 2, \ldots, n, t = 1, \ldots, T_j\}$ are independent. We assume this is approximately satisfied because these time series are sufficiently separated out in time as introduced in the beginning of this section. We provide corresponding numerical results   in Table \ref{dualshock}.}

\textcolor{red}{Under the dual shock setup, the donor pool size of this dataset is $n=2$. The fitted synthetic weight vector $\mbf{W}^*$ turns out to be $(0.756, 0.244)$. It implies that the March 15, 2008 time series is more similar to the time series of interest than the September 2008 time series. Similarly, we conducted sensitivity analysis using   $H = 2, 4, 6, 8$; and the results appear insensitive to $H$ from Table \ref{dualshock}. Based on Table \ref{dualshock}, $\hat{p}_1$ is uniformly 1 so that we fail to detect shock persistence. The results of voting and weighted voting are consistent to this with both voting for shock transience.}

\begin{table}[H]
	\caption{Results for Conoco Philips dual shock ($n=2$), $\mbf{W}^* = (0.756, 0.244)$ from scaled covariates} \label{dualshock}
\begin{center}
  \begin{tabular}{cccccccccr}
     $H$   &  $\hat{p}_1$ &   Vote   & weighted Vote  \\
     \hline 
     2  & 1    & 0  &0   \\ 
     4  & 1 & 0   &0   \\ 
     6   & 1  &0  & 0  \\ 
     8   & 1  & 0   & 0  
  \end{tabular}
\end{center}	
\end{table}

\textcolor{red}{ Unlike the results presented Table \ref{coptable}, we cannot know  the underlying $p_1$ and evaluate whether the voting and weighted voting are correct. This is due to the fact that the time series of interest experience financial and oil shocks at the same time. As a result,   the model is unidentifiable given the available  data. Nevertheless, the shock transience evident in Figure \ref{copshocktransience} provides a reference and supports our claim. This result confirms what we obtained in Section \ref{sptcop} and sucessfully generalizes the dual shock in post-shock prediction \citep{lin2021minimizing} to prevalence testing.}
